\bf Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-04-22 doc/paper.Rmd
crossvalidation files

```{r simulation, echo=FALSE}
library(MASS) 
Sigsame <- matrix(c(1, 0.85, 0.85, 1), nrow = 2) 
Sigdiff <- matrix(c(1, 0.12, 0.12, 1), nrow = 2) 
set.seed(20140501)
simu <- 1:10 %>% purrr::map_df(.f = function(i) {
  X1 <- mvrnorm(10000, mu = c(0,0), Sigma = Sigsame) 
  X2 <- mvrnorm(10000, mu = c(0,0), Sigma = Sigdiff) 
  Y1 <- pnorm(X1) 
  Y2 <- pnorm(X2) 
  wv <- 10*1:6

@@

```{r profile-sketch, fig.height = 4.5, fig.width='\\textwidth', fig.cap="Overview of the effect of different coarseness parameters $c$ on the profile shown in Figure \\ref{fig:sigs-profiles} (top). The bottom row shows histograms of  the (relative) optimal locations $t^o$ identified in the optimization step for different values of the coarseness parameter $c$. "}
profile <- sigs_graphics[[1]] %>% filter(land_id==19)
profile$lw10 <- lowess(x = profile$y, y = profile$value, f=.10)$y
profile$lw15 <- lowess(x = profile$y, y = profile$value, f=.15)$y
profile$lw20 <- lowess(x = profile$y, y = profile$value, f=.20)$y
profile$lw25 <- lowess(x = profile$y, y = profile$value, f=.25)$y
profile$lw30 <- lowess(x = profile$y, y = profile$value, f=.30)$y
#profile$lw50 <- lowess(x = profile$y, y = profile$value, f=.5)$y
#profile$lw75 <- lowess(x = profile$y, y = profile$value, f=.75)$y
#profile$lw100 <- lowess(x = profile$y, y = profile$value, f=1)$y

@@

\hh{Figure \ref{fig:coarse} shows the type II error rates for profiles using an optimization window $w_o= 120$ and a validation window $w_v = 30$ for varying level of coarseness. The type II error for all nominal levels of  $\alpha$ are the lowest for a coarseness range of 0.20 to 0.30, with a minimum in type II reached at a coarseness $c = 0.25$. The histograms suggest to use a value of coarseness below 0.2.}
\hh{However, for an optimal value of coarseness other aspects have to be condsidered.}
```{r coarse, fig.cap="Type II error with respect to coarseness parameter over profiles, $w_o = 120$, $w_v = 30$. Optimal values for coarseness are around $c \\approx 0.30$", fig.width=5, fig.height = 3, out.width='.6\\textwidth'}
e1<-errors2 %>% filter(wv==30)%>% ggplot(aes(x = coarse, y=beta, colour=factor(alpha))) +
  geom_point() + geom_line() +
  theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2") + xlab("Profile Coarseness")+
  ylab("Type II error") 
e1
```

>>>>

```{r simulation, echo=FALSE}
library(MASS) 
Sigsame <- matrix(c(1, 0.85, 0.85, 1), nrow = 2) 
Sigdiff <- matrix(c(1, 0.12, 0.12, 1), nrow = 2) 
set.seed(20140501)
simu <- 1:10 %>% purrr::map_df(.f = function(i) {
  X1 <- mvrnorm(10000, mu = c(0,0), Sigma = Sigsame) 
  X2 <- mvrnorm(10000, mu = c(0,0), Sigma = Sigdiff) 
  Y1 <- pnorm(X1)  # Probability Integral Transform
  Y2 <- pnorm(X2) 
  wv <- 10*1:6

@@

```{r profile-sketch, fig.height = 4, fig.width='\\textwidth', fig.cap="Overview of the effect of different coarseness parameters $c$ on the profile shown in Figure \\ref{fig:sigs-profiles} (top). The bottom row shows histograms of  the (relative) optimal locations $t^o$ identified in the optimization step for different values of the coarseness parameter $c$. "}
profile <- sigs_graphics[[1]] %>% filter(land_id==19)
profile$lw10 <- lowess(x = profile$y, y = profile$value, f=.10)$y
profile$lw15 <- lowess(x = profile$y, y = profile$value, f=.15)$y
profile$lw20 <- lowess(x = profile$y, y = profile$value, f=.20)$y
profile$lw25 <- lowess(x = profile$y, y = profile$value, f=.25)$y
profile$lw30 <- lowess(x = profile$y, y = profile$value, f=.30)$y
#profile$lw50 <- lowess(x = profile$y, y = profile$value, f=.5)$y
#profile$lw75 <- lowess(x = profile$y, y = profile$value, f=.75)$y
#profile$lw100 <- lowess(x = profile$y, y = profile$value, f=1)$y

@@

## Type II error rates

```{r}
files <- dir("../data/crossvalidate-cs2/")
cvcs2 <- data.frame()
for (file in files) {
  tmp <- readRDS(file.path("../data/crossvalidate-cs2/",file))
  cvcs2 <- rbind(cvcs2, tmp)
}
cvcs2$coarse <- cvcs2$coarseness
errorsCV <- 
  rbind(errorrate(cvcs2, 0.001), 
        errorrate(cvcs2, 0.005), 
        errorrate(cvcs2, 0.01), 
        errorrate(cvcs2, 0.05))

errorsCV %>% 
  ggplot(aes(x = wo, y = beta)) + 
  geom_point(aes(colour = factor(alpha))) +
  geom_line(aes(colour = factor(alpha))) +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2") +
  scale_shape_discrete(expression("Size of\nvalidation window "~w[v])) +
  xlab(expression("Window size for optimization "~w[o])) +
  ylab("Type II error rate") +
  theme_bw()

<!--
## Type II error rate and coarseness
\hh{Figure \ref{fig:coarse} shows the type II error rates for profiles using an optimization window $w_o= 120$ and a validation window $w_v = 30$ for varying level of coarseness. The type II error for all nominal levels of  $\alpha$ are the lowest for a coarseness range of 0.20 to 0.30, with a minimum in type II reached at a coarseness $c = 0.25$. The histograms suggest to use a value of coarseness below 0.2.}
\hh{However, for an optimal value of coarseness other aspects have to be condsidered.}
```{r coarse, fig.cap="Type II error with respect to coarseness parameter over profiles, $w_o = 120$, $w_v = 30$. Optimal values for coarseness are around $c \\approx 0.30$", fig.width=5, fig.height = 3, out.width='.6\\textwidth'}
e1<-errors2 %>% filter(wv==30)%>% ggplot(aes(x = coarse, y=beta, colour=factor(alpha))) +
  geom_point() + geom_line() +
  theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2") + xlab("Profile Coarseness")+
  ylab("Type II error") 
e1
```

-->

### 2018-04-22 doc/paper.tex
crossvalidation files

\hh{Figure \ref{fig:coarse} shows the type II error rates for profiles using an optimization window $w_o= 120$ and a validation window $w_v = 30$ for varying level of coarseness. The type II error for all nominal levels of  $\alpha$ are the lowest for a coarseness range of 0.20 to 0.30, with a minimum in type II reached at a coarseness $c = 0.25$. The histograms suggest to use a value of coarseness below 0.2.}
\hh{However, for an optimal value of coarseness other aspects have to be condsidered.}

{\centering \includegraphics[width=.6\textwidth]{figures/coarse-1}

\caption{Type II error with respect to coarseness parameter over profiles, $w_o = 120$, $w_v = 30$. Optimal values for coarseness are around $c \approx 0.30$}\label{fig:coarse}
\end{figure}

>>>>

\subsection{}\label{section}
